### 2022-08-03 ms/ms02_floats.tex
ENH improved boxplots instead of violin plots

\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_gwas.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_gwas.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_gwas.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_egene.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{e}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_egene.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{f}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_egene.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_etissue.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{h}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_etissue.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{i}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_scttr_count_per_rsid_etissue.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_egene_per_variant.py/vlnplt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_etissue_per_variant_egene.py/vlnplt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_gwas_per_variant_egene_etissue.py/vlnplt.png}
\end{subfigure}
%
\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:freq_gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
%
\includegraphics[width=\textwidth]{\floatRelativePath/plt_bxplt_remaptf_per_rsid.py/bxplt_remaptf_per_rsid_flank_50.png}
\end{subfigure}
%
\caption{\textbf{Binding of transcription factors in the region (100 kb) around pleiotropic variants.} (\textbf{a}) TODO.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 7: beta
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_beta_pval.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_violin_beta_pval.py/gwas_beta.png}
\end{subfigure}
%
\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:beta}
%
\end{figure*}

>>>>

\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{e}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{f}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start132239645_end132497907_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{h}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr6_start31034839_end32478149_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{i}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr12_start111395984_end111645358_categories11.png}
\end{subfigure}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{\textbf{Frequency of eGenes per variant, eTissues per variant-eGene and phenotypes per variant-eGene-eTissue.} (\textbf{a}) TODO.} \label{fig:freq_gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remaptf.py/bxplt_remaptf_per_rsid_flank_0.png}
\end{subfigure}
%
\caption{\textbf{Binding of transcription factors in the region (100 kb) around pleiotropic variants.} (\textbf{a}) TODO.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 7: beta and log pval
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_beta.py/gwas_beta.png}
\end{subfigure}

\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_logpval.py/eqtl.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_gwas_cat_y_logpval.py/gwas.png}
\end{subfigure}

\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:beta}
%
\end{figure*}
